---
title             : "Reproduced Report: For 5-Month-Old Infants, Melodies Are Social"
shorttitle        : "Reproduced: Melodies are Social for Infants"

author: 
  - name          : "Ana Lakshin"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "2900 Bedford Ave, Brooklyn, NY 11210"
    email         : "Ana.Lakshin09@bcmail.brooklyn.cuny.edu"

affiliation:
  - id            : "1"
    institution   : "Brooklyn College"

authornote: |
  Psychology Department of Brooklyn College.
  Psych 7709

abstract: |
  Using Mehr et. al (2016)'s original data the following will be a reproduction of the first experiment's analyses. The study used 5 month old infants, two songs differing in familiarity and two unfamiliar singers to determine if familiarity with a song will result in longer looking times at the unfamiliar singer. It was found that infants gazed at the unfamiliar person singing a familiar song longer than at the new person singing an unfamiliar song.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "music, social cognition, reproduced report, memory"
wordcount         : "X"

bibliography      : ["biblio.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---


```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods

## Participants
There were 38 full-term infants and their parents from the greater Boston area. 
## Procedure
Parents learned to sing one of two new songs. They sang one of the songs to their infants on a regular basis. After 1 to 2 weeks of song exposure, the infants returned to the lab for a selective-attention test. During the baseline trial of the test, two unfamiliar individuals silently smiled at the infant for a brief period of time after which each individual sang one of the two songs. After one sang the familiar and the other sang the unfamiliar song, the two would again silently smile and gaze at the infant. 

## Data analysis
We used `r cite_r("biblio.bib")` for all our analyses.


# Results

```{r, Baseline}
library(data.table)
all_data <- read.csv(file = "MehrData.csv")
keep<- c() 
#all_data<- data.frame(keep)
library(dplyr)

baseline<- all_data %>%
  filter(Baseline_Proportion_Gaze_to_Singer, exp1==1)

baseline<-baseline$Baseline_Proportion_Gaze_to_Singer

mean_exp1<- mean(baseline)  
SD_exp1<- sd(baseline)

exp1T<-t.test(baseline, mu=.5)


```
In the baseline condition, there was no difference in gazes to either singer. The mean looking time of the familiar song's singer was `r mean_exp1 * 100`% (SD = `r SD_exp1`) which was not significantly different from chance according to the one sample T-Test `r apa_print(exp1T)$statistic`.

```{r,Familiarization Stage}
familiarization<- all_data %>%
  filter(Familiarization_Gaze_to_Familiar, exp1 == 1) %>%
  filter(Familiarization_Gaze_to_Unfamiliar, exp1 == 1)%>%
  mutate(mean_fam = Familiarization_Gaze_to_Familiar/1000,
         mean_unfam = Familiarization_Gaze_to_Unfamiliar/1000)

fam_to_fam<- familiarization$Familiarization_Gaze_to_Familiar
fam_to_unfam <- familiarization$Familiarization_Gaze_to_Unfamiliar

x<- c(rep(1000,31))
fam_to_fam<- fam_to_fam/x
fam_to_unfam<- fam_to_unfam/x

M_ftf<- mean(fam_to_fam)
SD_ftf<- sd(fam_to_fam)

M_ftuf<- mean(fam_to_unfam)
SD_ftuf<- sd(fam_to_unfam)


```
The familiarization stage was unsuccessfully replicated. Original results claim the duration of gazing at the singer of the familiar song had a mean of 15.6 s with a standard deviation of 5.07. Reproduced mean was `r M_ftf` with standard deviation of `r SD_ftf`. For duration of gazing at singers of the unfamiliar song, the original study reported a mean of 15.3 s and standard deviation 5.10. Reproduced mean was `r M_ftuf` with standard deviation of `r SD_ftuf`. 


```{r, Test Phase}
testing<- all_data %>%
  filter(Test_Proportion_Gaze_to_Singer, exp1==1)
test<-testing$Test_Proportion_Gaze_to_Singer

mean_test<- mean(test)
SD_test<- sd(test)

expTest<- t.test(test, mu=.5)

```
During test phase, the infants looked at the silently smiling singer of the familiar song significantly more than chance (M= `r mean_test`, SD = `r SD_test`) `r apa_print(expTest)$statistic`.

```{r, comment = "Paired Samples T-Test"}
difference<- t.test(baseline,test,paired = TRUE, var.equal = TRUE)

```
Also, during test phase the proportion of time during which the infants gazed at the singer of the familiar song was greater than the duration during baseline (`r apa_print(difference)$statistic`)`.

```{r}
library(ggplot2)
library(ggsignif)
Phase <- rep(c("Baseline","Test"), each = 32)
Proportions <- c(baseline,test)
graph1 <- data.frame(Phase,Proportions)
ggplot(graph1, aes(x=Phase, y=Proportions))+
  geom_hline(yintercept = .5, linetype = "dashed")+
  geom_boxplot(fill = "blue", width=.3)+
  theme_classic(base_size = 12)+
  geom_signif(comparisons = list(c("Baseline","Test")),
              map_signif_level = TRUE, textsize = 6)+
  coord_cartesian(ylim = c(0,1))+
  scale_y_continuous(breaks=c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1.0))+
  scale_x_discrete(labels= c("Before Singing (Baseline)","After Singing (Test)"),)
  


```

```{r}
library(ggplot2)
library(ggsignif)
Phase <- rep(c("Baseline","Test"), each = 32)
Proportions <- c(baseline,test)
graph1 <- data.frame(Phase,Proportions)
ggplot(graph1, aes(x=Phase, y=Proportions))+
  geom_hline(yintercept = .5, linetype = "dashed")+
  geom_boxplot(fill = "blue", width=.3)+
  theme_classic(base_size = 12)+
  stat_signif(test = "t.test")+
  geom_signif(y_position = c(1,2), xmin = c(1,2), xmax = c(2.1,2),
              annotations = c("*","NS"))+
  geom_signif(comparisons = list(c("Baseline","Test")))+
  coord_cartesian(ylim = c(0,1))+
  scale_y_continuous(breaks=c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1.0))+
  scale_x_discrete(labels= c("Before Singing (Baseline)","After Singing (Test)"),)
  
  

```
# Discussion
Re-analysis was successful for baseline and test phase. It was not successful for familiarization phase and for display of significance on graph. 
Also, something is wrong with the bibliography file 

## Simulation-Based Power Analysis
```{r}
sim_power <- function(x){
  A <- rnorm(n=32,mean=0, sd=1)
  B <- rnorm(n=32,mean=(0+x), sd=1)
  return(t.test(A,B,paired = TRUE, var.equal=TRUE)$p.value)
}

effect_sizes <- seq(.1,2,.1)

power <- sapply(effect_sizes, 
          FUN = function(x) {
            sims <- replicate(10000,sim_power(x))
            sim_power <- length(sims[sims<.05])/length(sims)
            return(sim_power)})

plot_df <- data.frame(effect_sizes,power)

ggplot(plot_df, aes(x=effect_sizes,
                    y=power))+
  geom_point()+
  geom_line()

```


\newpage

# References
```{r create_r-references}
r_refs(file = "biblio.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
